---
title: "Appendix S3 Model syntax and detailed output summaries for the meta-analysis models."
output:
  bookdown::pdf_document2:
    reference_docx: template.docx
    number_sections: true
    toc: true
link-citations: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",")
})
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
load(file = "../models/obj1/m1.Rdata")
load(file = "../models/obj2/m2.1.Rdata")
load(file = "../models/obj2/m2.2.Rdata")
load(file = "../models/obj2/m2.3.Rdata")
load(file = "../models/obj2/m2.4.Rdata")
load(file = "../models/obj2/m2.5.Rdata")
load(file = "../models/obj2/m2.6.Rdata")
load(file = "../models/obj2/m2.7.Rdata")
load(file = "../models/obj2/m2.8.Rdata")
```

# Model for the first prediction (delayed seed germination should correlate with species adapted to high stress and low disturbance)

## Model for all species

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m1)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m1)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m1$VCV[,"animal"]/(m1$VCV[,"animal"] + m1$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m1)
```

# Models for the second prediction (the specific germination cues driving delayed seed germination should vary depending on the species preferences for stress and disturbance)

## Model for the low stress - low disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.1)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.1)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.1$VCV[,"animal"]/(m2.1$VCV[,"animal"] + m2.1$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.1)
```

## Model for the low stress - high disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.2)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.2)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.2$VCV[,"animal"]/(m2.2$VCV[,"animal"] + m2.2$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.2)
```

## Model for the drought stress - low disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.3)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.3)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.3$VCV[,"animal"]/(m2.3$VCV[,"animal"] + m2.3$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.3)
```

## Model for the drought stress - high disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.4)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.4)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.4$VCV[,"animal"]/(m2.4$VCV[,"animal"] + m2.4$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.4)
```

## Model for the cold stress - low disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.5)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.5)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.5$VCV[,"animal"]/(m2.5$VCV[,"animal"] + m2.5$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.5)
```

## Model for the cold stress - high disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.6)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.6)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.6$VCV[,"animal"]/(m2.6$VCV[,"animal"] + m2.6$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.6)
```

## Model for the wetlands - low disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.7)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.7)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.7$VCV[,"animal"]/(m2.7$VCV[,"animal"] + m2.7$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.7)
```

## Model for the wetlands - high disturbance group

### Model summary

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.8)
```

### Random effects

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.8)$Gcovariances
```

### Phylogenetic signal

```{r message = FALSE, echo = FALSE, warning = FALSE}
lambda <- m2.8$VCV[,"animal"]/(m2.8$VCV[,"animal"] + m2.8$VCV[,"units"])
data.frame(
  lambda = mean(lambda) %>% round(2),
  min = coda::HPDinterval(lambda)[, 1] %>% round(2),
  max = coda::HPDinterval(lambda)[, 2] %>% round(2))
```

### Model diagnostic plots

```{r message = FALSE, echo = FALSE, warning = FALSE}
plot(m2.8)
```