---
title: "Appendix S1 Model output summaries for the MCMCglmms."
output:
  bookdown::pdf_document2:
    reference_docx: template.docx
    number_sections: false
    toc: false
link-citations: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",")
})
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
load(file = "../models/obj1/m1.B.Rdata")
load(file = "../models/obj2/m2.1.Rdata")
load(file = "../models/obj2/m2.2.Rdata")
load(file = "../models/obj2/m2.3.Rdata")
load(file = "../models/obj2/m2.4.Rdata")
load(file = "../models/obj2/m2.5.Rdata")
load(file = "../models/obj2/m2.6.Rdata")
load(file = "../models/obj2/m2.7.Rdata")
load(file = "../models/obj2/m2.8.Rdata")
```

## 1. Model for the first prediction (delayed seed germination should correlate with species adapted to high stress and low disturbance)

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m1.B)
```

## 2. Models for the second prediction (the specific germination cues driving delayed seed germination should vary depending on the species preferences for stress and disturbance)

### 2.1 Model for the low stress - low disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.1)
```

### 2.2 Model for the low stress - high disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.2)
```

### 2.3 Model for the water stress - low disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.3)
```

### 2.4 Model for the water stress - high disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.4)
```

### 2.5 Model for the cold stress - low disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.5)
```

### 2.6 Model for the cold stress - high disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.6)
```

### 2.7 Model for the wetlands - low disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.7)
```

### 2.8 Model for the wetlands - high disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.8)
```