---
title: "Appendix S2 Model output summaries for the MCMCglmms."
output:
  bookdown::pdf_document2:
    reference_docx: template.docx
    number_sections: false
    toc: false
link-citations: yes
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",")
})
```

```{r message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
load(file = "../models/obj1/m1.Rdata")
load(file = "../models/obj2/m2.LL.Rdata")
load(file = "../models/obj2/m2.HL.Rdata")
load(file = "../models/obj2/m2.LH.Rdata")
load(file = "../models/obj2/m2.HH.Rdata")
```

## 1. Model for the first prediction (delayed seed germination should correlate with species adapted to high stress and low disturbance)

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m1)
```

## 2. Models for the second prediction (the specific germination cues driving delayed seed germination should vary depending on the species preferences for stress and disturbance)

### 2.1 Model for the low stress - low disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.LL)
```

### 2.2 Model for the high stress - low disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.HL)
```

### 2.3 Model for the low stress - high disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.LH)
```

### 2.4 Model for the high stress - high disturbance group

```{r message = FALSE, echo = FALSE, warning = FALSE}
summary(m2.HH)
```